---
title: "A3 - Student Tattoo Attraction Preferences by Gender"
format: html
author: Jashith S Kumar
description: A survey dataset of student-reported ratings for three television series—Friends, Modern Family, and The Big Bang Theory.
---

## Data Dictionary

A tibble with 40 observations and 3 variables:

## Qualitative Variables:

> -   **name** Name of the respondent (mostly unique, factor)
> -   **gender** Gender of the respondent (factor, e.g., "M", "F")
> -   **tattoo_attractive** Response to "Do you find tattoos attractive?" ("Yes" or "No", factor)

## Quantitative Variables:
> -   *None in this dataset; all variables are qualitative/categorical (no direct quantitative variable like age or counts).*

## Loads all R packages needed for data munging, visualization, and analysis

```{r}
library(tidyverse)
library(mosaic) # Our all-in-one package
library(skimr) # Looking at data
library(visdat) # Mapping missing data
library(naniar) # Missing data visualization and munging
library(janitor) # Clean the data
library(tinytable) # Printing Tables for our data
library(ggformula)
library(ggplot2)
library(ggpubr) 
library(janitor)
library(rstatix)
library(vcd)
```

## Reads the ratings data from CSV and standardizes the column names to snake_case

```{r}
tat <- readr::read_csv("../data/tattoo_attraction.csv") %>% 
janitor::clean_names(case = "snake")
```

## Shows the number of rows and columns in the dataset

```{r}
dim(tat)
```

## Lists the column names in the dataset

```{r}
base::names(tat)
```

## Visualizes missing data and overall structure using the visdat package

```{r}
visdat::vis_miss(tat)
visdat::vis_dat(tat, sort_type = TRUE, palette = "cb_safe")
```

## Cleans, standardizes, and removes missing data, then previews the dataframe

```{r}
tat_modified <- tat %>%
  naniar::replace_with_na_all(condition = ~ .x %in% common_na_numbers) %>%
  replace_with_na_all(condition = ~ .x %in% common_na_strings)

tat_modified <- tat_modified %>% drop_na()
glimpse(tat_modified)
```

##  Builds a contingency table for tattoo attractiveness preference by gender and visualizes it using a grouped bar chart

```{r}
tat_modified <- tat_modified %>%
  mutate(
    name = as.factor(name),
    gender = as.factor(gender),
    tattoo_attractive = as.factor(tattoo_attractive)
  )

glimpse(tat_modified)
```

## Displaying the cleaned data in a table for inspection

```{r}
tat_modified %>%
  DT::datatable(
    style = "default",
    caption = htmltools::tags$caption(
      style = "caption-side: top; text-align: left; color: black; font-size: 100%;", "are tatoos attractive"
    ),
    options = list(pageLength = 10, autoWidth = TRUE)
  ) %>%
  DT::formatStyle(
    columns = names(tat_modified),
    fontFamily = "Roboto Condensed",
    fontSize = "12px"
  )
```

## Calculating and reports mean and standard deviation for each show’s ratings

```{r}
tab <- table(tat_modified$tattoo_attractive, tat_modified$gender)

barplot(tab,
        beside = TRUE,
        col = c("skyblue", "orange"),
        legend.text = TRUE,
        args.legend = list(title = "like tatoos", x = "topright"),
        main = "Tattoo Attraction by Gender",
        xlab = "Is Tattoo Attractive?",
        ylab = "Count")


```



##  total bar graph of tattoo attractiveness preference (regardless of gender)

```{r}
totals <- table(tat_modified$tattoo_attractive)

barplot(totals,
        col = c("grey80", "darkolivegreen3"),
        main = "Total Tattoo Attractiveness Preference",
        xlab = "Is Tattoo Attractive?",
        ylab = "Number of Respondents")
```

