---
title: " A3 - Student Ratings of Three Popular TV Series: Friends, Modern Family, and The Big Bang Theory"
format: html
author: Jashith S Kumar
description: A survey dataset of student-reported ratings for three television series—Friends, Modern Family, and The Big Bang Theory.
---

## Data Dictionary

A tibble with 52 observations and 5 variables:

## Qualitative Variables:

> -   name: Name of the respondent (mostly unique, factor).

> -   gender: Gender of the respondent (factor, e.g., "Male", "Female").

## Quantitative Variables:

> -   friends: Student rating for 'Friends' (integer, scale 1–10).

> -   modern_family: Rating for 'Modern Family' (integer, scale 1–10).

> -   big_bang_theory: Rating for 'Big Bang Theory' (integer, scale 1–10).

## Loads all R packages needed for data munging, visualization, and analysis

```{r}
library(tidyverse)
library(mosaic) # Our all-in-one package
library(skimr) # Looking at data
library(visdat) # Mapping missing data
library(naniar) # Missing data visualization and munging
library(janitor) # Clean the data
library(tinytable) # Printing Tables for our data
library(ggformula)
library(ggplot2)
library(ggpubr) 
library(janitor)
library(rstatix)
```

## Reads the ratings data from CSV and standardizes the column names to snake_case

```{r}
tv_series <- readr::read_csv("../data/tv_series.csv") %>% 
janitor::clean_names(case = "snake")
```

## Shows the number of rows and columns in the dataset

```{r}
dim(tv_series)
```

## Lists the column names in the dataset

```{r}
base::names(tv_series)
```

## Visualizes missing data and overall structure using the visdat package

```{r}
visdat::vis_miss(tv_series)
visdat::vis_dat(tv_series, sort_type = TRUE, palette = "cb_safe")
```

## Cleans, standardizes, and removes missing data, then previews the dataframe

```{r}
tv_series_modified <- tv_series %>%
  naniar::replace_with_na_all(condition = ~ .x %in% common_na_numbers) %>%
  replace_with_na_all(condition = ~ .x %in% common_na_strings)

tv_series_modified <- tv_series_modified %>% drop_na()
glimpse(tv_series_modified)
```

## Converts name and gender to factor types and previews the updated dataframe

```{r}
tv_series_modified <- tv_series_modified %>%
  mutate(
    name = as.factor(name),
    gender = as.factor(gender)
  )

glimpse(tv_series_modified)
```

## Displays the cleaned data in a table for inspection

```{r}
tv_series_modified %>%
  DT::datatable(
    style = "default",
    caption = htmltools::tags$caption(
      style = "caption-side: top; text-align: left; color: black; font-size: 100%;", "prefernce in popular tv series"
    ),
    options = list(pageLength = 10, autoWidth = TRUE)
  ) %>%
  DT::formatStyle(
    columns = names(tv_series_modified),
    fontFamily = "Roboto Condensed",
    fontSize = "12px"
  )
```

## Calculates and reports mean and standard deviation for each show’s ratings

```{r}
tibble(
  friends_mean = mean(tv_series_modified$friends),
  friends_sd = sd(tv_series_modified$friends),
  modern_family_mean = mean(tv_series_modified$modern_family),
  modern_family_sd = sd(tv_series_modified$modern_family),
  big_bang_mean = mean(tv_series_modified$big_bang_theory),
  big_bang_sd = sd(tv_series_modified$big_bang_theory)
)


```

## Visualizes the distribution of ratings for each show as boxplots

```{r}
boxplot(tv_series_modified$friends,
        tv_series_modified$modern_family,
        tv_series_modified$big_bang_theory,
        names = c("Friends", "Modern Family", "Big Bang Theory"),
        col = c("skyblue", "orange", "purple"),
        ylab = "Rating",
        main = "TV Show Ratings")

```

## Displays mean ratings across shows as a bar graph

```{r}
means <- c(mean(tv_series_modified$friends),
           mean(tv_series_modified$modern_family),
           mean(tv_series_modified$big_bang_theory))
shows <- c("Friends", "Modern Family", "Big Bang Theory")
barplot(means, names.arg = shows, col = c("skyblue", "orange", "purple"),
        ylab = "Mean Rating", main = "Mean Ratings for TV Shows")

```

## Performs repeated measures ANOVA to test if mean ratings differ by show

```{r}
id <- seq_len(nrow(tv_series_modified))
ratings_matrix <- as.matrix(tv_series_modified[,c("friends", "modern_family", "big_bang_theory")])
long <- stack(tv_series_modified[,c("friends", "modern_family", "big_bang_theory")])
long$id <- rep(id, 3)
long$series <- rep(c("friends", "modern_family", "big_bang_theory"), each = nrow(tv_series_modified))
anova_results <- aov(values ~ factor(series) + Error(id/factor(series)), data = long)
summary(anova_results)


```

## Creates a pie chart showing the most preferred show (highest rating) for each respondent

```{r}
highest <- apply(tv_series_modified[,c("friends", "modern_family", "big_bang_theory")], 1, function(row) {
  c("Friends", "Modern Family", "Big Bang Theory")[which.max(row)]
})
pie(table(highest),
    col = c("skyblue", "orange", "purple"),
    main = "Most Preferred Show (Highest Rating)")


```

## Draws a grouped barplot showing mean ratings for each show split by gender

```{r}
friends_means <- tapply(tv_series_modified$friends, tv_series_modified$gender, mean)
modern_means  <- tapply(tv_series_modified$modern_family, tv_series_modified$gender, mean)
bigbang_means <- tapply(tv_series_modified$big_bang_theory, tv_series_modified$gender, mean)
means_matrix <- rbind(friends_means, modern_means, bigbang_means)
rownames(means_matrix) <- c("Friends", "Modern Family", "Big Bang Theory")

barplot(means_matrix,
        beside = TRUE,
        col = c("skyblue", "orange", "purple"),
        legend.text = TRUE,
        args.legend = list(title = "Gender", x = "topright"),
        ylab = "Mean Rating",
        main = "Mean TV Show Ratings by Gender")
```
