---
title: "A3 - Are Srishti Dads Weird?"
format: html
author: Jashith S Kumar
description: This dataset records the responses of 65 university students from two colleges (MIT and Srishti/SMI) to a survey asking whether they believe their dads are weird. For each student, the dataset captures their gender, college affiliation, unique name, and a Yes/No response to the question "Is your dad weird?" The data is strictly categorical, enabling comparison of perceived dad weirdness across gender and institutional groupings.
---

## Data dictionary

A tibble with 65 observations and 4 variables:

## Qualitative Variables:

> -   **gender** Gender of the student (factor with 3 levels: "M", "F", "Other" or similar).
> -   **college** College of the student (factor with 2 levels: "MIT", "SMI"/"Srishti").
> -   **is_dad_weird** Student perception of their dad as weird (factor with 2 levels: "Yes", "No").
> -   **name** Name of the student (character, mostly unique).

## Quantitative Variables:

> -   *None in this dataset; all variables are qualitative/categorical (no direct quantitative variable like age or counts).*

## loading all packages needed for data munging, visualization, and statistical analysis

```{r}
library(tidyverse)
library(mosaic) # Our all-in-one package
library(skimr) # Looking at data
library(visdat) # Mapping missing data
library(naniar) # Missing data visualization and munging
library(janitor) # Clean the data
library(tinytable) # Printing Tables for our data
library(ggformula)
library(vcd)

```

## reading the CSV file with the survey data

```{r}
weird_dads <- readr::read_csv("../data/weird_dads.csv")
```

## inspecting dimensions and column names

```{r}
dim(weird_dads)
base::names(weird_dads)
```

## visualizing missing entries to highlight incomplete data and help with cleaning

```{r}
visdat::vis_miss(weird_dads)
visdat::vis_dat(weird_dads, sort_type = TRUE, palette = "cb_safe")
```

## Replacing common missing value codes with true NA, drops rows with any NA

```{r}
weird_dads_modified <- weird_dads %>%
  naniar::replace_with_na_all(condition = ~ .x %in% common_na_numbers) %>%
  replace_with_na_all(condition = ~ .x %in% common_na_strings)

weird_dads_modified <- weird_dads_modified %>% drop_na()
glimpse(weird_dads_modified)
```

```{r}
weird_dads_modified <- weird_dads_modified %>%
  mutate(
    gender = as.factor(gender),
    college = as.factor(college),
    is_dad_weird = as.factor(is_dad_weird),
    name = as.factor(name)
  )

glimpse(weird_dads_modified)
```

## Displaying the cleaned dataset

```{r}
weird_dads_modified %>%
  DT::datatable(
    style = "default",
    caption = htmltools::tags$caption(
      style = "caption-side: top; text-align: left; color: black; font-size: 100%;", "SMI Dads Weird"
    ),
    options = list(pageLength = 10, autoWidth = TRUE)
  ) %>%
  DT::formatStyle(
    columns = names(weird_dads_modified),
    fontFamily = "Roboto Condensed",
    fontSize = "12px"
  )
```

## Bar chart showing students saying their dad is weird, split by gender

```{r}
gf_bar(~is_dad_weird | gender, data = weird_dads_modified, fill = ~is_dad_weird, palette = "Dark")


```

## Mosaic plots visualizing the relationships between gender and weird dad perception separately in each college

```{r}
# For MIT college only
mit_data <- weird_dads_modified %>% filter(college == "MIT")
mosaicplot(~ gender + is_dad_weird, data = mit_data, color = TRUE, main = "MIT: Gender vs Weird Dad Perception")

# For SMI/Srishti college only
smi_data <- weird_dads_modified %>% filter(college == "SMI")
mosaicplot(~ gender + is_dad_weird, data = smi_data, color = TRUE, main = "SMI: Gender vs Weird Dad Perception")

```

## Cross-tab of college vs weird dad response to summarize group frequencies for statistical analysis.

```{r}
tab <- table(weird_dads_modified$college, weird_dads_modified$is_dad_weird)
print(tab)
```

## Chi-square test on the contingency table to statistically assess whether weird dad perception varies significantly across colleges

```{r}
chisq.test(tab)
```

## Bar chart of proportions of "yes"/"no" responses in each college to visually compare group percentages

```{r}
gf_bar(~is_dad_weird | college, data = weird_dads_modified, fill = ~is_dad_weird, position = "fill")

```

## Mosaic of college vs weird dad response distribution.

```{r}


tab <- table(weird_dads_modified$college, weird_dads_modified$is_dad_weird)


mosaic(~ college + is_dad_weird, data = weird_dads_modified,
       shade = TRUE,
       main = "Dads are Weird: MIT vs SMI")
```
